The 2018 heatwave and its implications on ozone induced damage on vegetation in a subarctic climate

### 2020-10-09 VegOzone.tex
Added appendix plot for BGS/EGS estiate for coniferous trees from MODIS data.

@@

\authorcontribution{SF has written the manuscripted, collected and processed ozone and environmental data, and performed all statistical analyses. AVV has performed on-site observation of vegetation demage induced by ozone and contributed to theory of ozone interaction with vegetation within the introduction. LE... CO... ALEB...  FS... TB... All authors contributed to discussion and conclusion of the results.} %% this section is mandatory

>>>>

\begin{figure*}[t]
  \includegraphics[width=12cm]{modis_Psn}
  \caption{Estimated begin (BGS) and end (EGS) of growing season for coniferous trees from MODIS Aqua/Terra net photosynthesis (PSN) product. A $1\times 1\,\unit{km}$ area around Svanhovd was selected. Daily averaged data for both 2018 and 2019 has been fitted with a quadratic polynomial function. The numerically computed root yields: BGS 122/106 day of year and EGS 261/274 day of year for 2018/2019, respectively.}
  \label{fig:modis_Psn}
\end{figure*}

@@

\authorcontribution{SF has written the manuscript, collected and processed ozone and environmental data, and performed all statistical analyses. AVV has performed on-site observation of vegetation damage induced by ozone and contributed to theory of ozone interaction with vegetation within the introduction. LE... CO... ALEB...  FS... TB... All authors contributed to discussion and conclusion of the results.} %% this section is mandatory
